Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany

### 2024-04-18 paper/paper.qmd
use style to modify

cleaned_aerial_priority |>
  head() |>
  kable(booktabs = TRUE, align = "c"
)
```
@tbl-aerial_preview presents the first six rows from the cleansed dataset, focusing on aerial bombing missions conducted by the Allies against German industries during WWII.

@@

# Update the color set based on the new requirements
priority_colors <- c("primary target" = "#FF0000",
                     "secondary target" = "#00BA38",
                     "target of opportunity" = "#619CFF",
                     "target of last resort" = "coral")

@@

# Define the specified colors for each priority level
priority_colors <- c("primary target" = "#FF0000",  # Red
                     "secondary target" = "#00BA38",  # Green
                     "target of opportunity" = "#619CFF",  # Blue
                     "target of last resort" = "#FF7F50")  # Coral

@@

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

# Print the summary of the model to inspect the results
print(summary(aerial_priority_model))
prior_summary(aerial_priority_model)

```

@@

# Create a data frame containing the model's coefficient summary
model_summary_df <- data.frame(
  Parameter = c(
    'Railway infrastructure',
    'Synthetic oil refineries',
    'Unidentified targets',
    'Urban areas',
    'Other countries',
    'USA',
    'Bomb',
    'Aircraft',
    'Intercept 1 (last resort|opportunity)',
    'Intercept 2 (opportunity|secondary)',
    'Intercept 3 (secondary|primary)'
  ),
  Mean = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
  SD = c(0.1, 0.1, 0.1, 0.1, 0.3, 0.3, 0.0, 0.0, 0.4, 0.3, 0.3),
  `10%` = c(-1.6, -0.2, -3.5, -1.6, 0.4, 0.5, 0.0, 0.1, -4.1, -1.4, 0.0),
  `50%` = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
  `90%` = c(-1.3, 0.1, -3.2, -1.3, 1.2, 1.3, 0.0, 0.1, -3.2, -0.5, 0.9)
)

# Use kable to create and style the table
kable(model_summary_df, format = "markdown", align = 'c', col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%"))

```

@@

# Plot the 90% credible intervals for all model coefficients
# This visualizes the impact of each predictor on the ordered priority levels
mcmc_intervals(posterior, prob = 0.9) +
  labs(title = "Model Coefficients",
       subtitle = "90% credible intervals",
       x = "Coefficient Estimate",
       y = "Parameters")+
  theme(
    plot.title = element_text(hjust = 0.5),    # Center the main title
    plot.subtitle = element_text(hjust = 0.5)  # Center the subtitle
  )

```

@@

# Plot the posterior distributions for all parameters to assess their influence on priority levels
mcmc_areas(posterior) +
  labs(title = "Posterior Distributions of Model Parameters",
       subtitle = "Assessing the influence of predictors on ordered target priority",
       x = "Parameter Value",
       y = "Density")

```

>>>>

cleaned_aerial_priority |>
  head() |>
  kable(booktabs = TRUE, align = "c")
```
@tbl-aerial_preview presents the first six rows from the cleansed dataset, focusing on aerial bombing missions conducted by the Allies against German industries during WWII.

@@

# Update the color set based on the new requirements
priority_colors <- c(
  "primary target" = "#FF0000",
  "secondary target" = "#00BA38",
  "target of opportunity" = "#619CFF",
  "target of last resort" = "coral"
)

@@

# Define the specified colors for each priority level
priority_colors <- c(
  "primary target" = "#FF0000", # Red
  "secondary target" = "#00BA38", # Green
  "target of opportunity" = "#619CFF", # Blue
  "target of last resort" = "#FF7F50"
) # Coral

@@

@@

# Print the summary of the model to inspect the results
print(summary(aerial_priority_model))
prior_summary(aerial_priority_model)
```

@@

# Create a data frame containing the model's coefficient summary
model_summary_df <- data.frame(
  Parameter = c(
    "Railway infrastructure",
    "Synthetic oil refineries",
    "Unidentified targets",
    "Urban areas",
    "Other countries",
    "USA",
    "Bomb",
    "Aircraft",
    "Intercept 1 (last resort|opportunity)",
    "Intercept 2 (opportunity|secondary)",
    "Intercept 3 (secondary|primary)"
  ),
  Mean = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
  SD = c(0.1, 0.1, 0.1, 0.1, 0.3, 0.3, 0.0, 0.0, 0.4, 0.3, 0.3),
  `10%` = c(-1.6, -0.2, -3.5, -1.6, 0.4, 0.5, 0.0, 0.1, -4.1, -1.4, 0.0),
  `50%` = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
  `90%` = c(-1.3, 0.1, -3.2, -1.3, 1.2, 1.3, 0.0, 0.1, -3.2, -0.5, 0.9)
)

# Use kable to create and style the table
kable(model_summary_df, format = "markdown", align = "c", col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%"))
```

@@

# Plot the 90% credible intervals for all model coefficients
# This visualizes the impact of each predictor on the ordered priority levels
mcmc_intervals(posterior, prob = 0.9) +
  labs(
    title = "Model Coefficients",
    subtitle = "90% credible intervals",
    x = "Coefficient Estimate",
    y = "Parameters"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5), # Center the main title
    plot.subtitle = element_text(hjust = 0.5) # Center the subtitle
  )
```

@@

# Plot the posterior distributions for all parameters to assess their influence on priority levels
mcmc_areas(posterior) +
  labs(
    title = "Posterior Distributions of Model Parameters",
    subtitle = "Assessing the influence of predictors on ordered target priority",
    x = "Parameter Value",
    y = "Density"
  )
```
